Correcting K-correction: dark energy is based on a math error from 1930

### 2025-01-06 paper/dark_energy_corrections.tex
Fix missing parens

\begin{figure}
  \plotone{k_equation_flow.pdf}
  \caption{The ratio $K'_{xy}$ is the crux of the K-correction algorithm. We
  are able to observe a SnIa in the redshifted observation frame, but we want
  to compute the magnitude in the rest frame as if no redshift has occurred.
  This computation starts with $F(\lambda$, the spectral energy density, which
  we then convert to $F'(\lambda)$, the photon density for the rest frame. We
  show the process of computing $R'(\lambda$, the photon density in the
  observation frame, in three phases starting at the top right of the figure.
  First we stretch the photon density, but this step inflates counts. In the
  second step, we correct for the inflated counts by multiplying by $1/(1+z)$;
  at this point, the total count equals the total count of $F'(\lambda)$.
  Finally, in the third step we finish calculating the observation frame photon
  density $R'(\lambda)$ by accounting for time dilation, which also reduces
  photon counts by a factor of $1/(1+z)$. We can compute the expected ratio of
  photons by totalling the area under the curves in the bottom two panels. This
  example does not show the process of converting photon flux to magnitude, nor
  does it address the zero-point correction.
  }
  \label{fig:k-example}
\end{figure}

>>>>

\begin{figure}
  \plotone{k_equation_flow.pdf}
  \caption{The ratio $K'_{xy}$ is the crux of the K-correction algorithm. We
  are able to observe a SnIa in the redshifted observation frame, but we want
  to compute the magnitude in the rest frame as if no redshift has occurred.
  This computation starts with $F(\lambda)$, the spectral energy density, which
  we then convert to $F'(\lambda)$, the photon density for the rest frame. We
  show the process of computing $R'(\lambda)$, the photon density in the
  observation frame, in three phases starting at the top right of the figure.
  First we stretch the photon density, but this step inflates counts. In the
  second step, we correct for the inflated counts by multiplying by $1/(1+z)$;
  at this point, the total count equals the total count of $F'(\lambda)$.
  Finally, in the third step we finish calculating the observation frame photon
  density $R'(\lambda)$ by accounting for time dilation, which also reduces
  photon counts by a factor of $1/(1+z)$. We can compute the expected ratio of
  photons by totalling the area under the curves in the bottom two panels. This
  example does not show the process of converting photon flux to magnitude, nor
  does it address the zero-point correction.
  }
  \label{fig:k-example}
\end{figure}
